Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-07-23 exp1/iswc2013.tex
Move host+port number stuff to Review 4
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@614 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{center}\small
  \begin{tabular}{|@{~~}p{0.40\textwidth}|@{~~}p{0.53\textwidth}|}
    \hline
    \textbf{``Union''} & \textbf{``Lang''} \\[-2ex]
    \verbatiminput{experiment/Union-2} &
    \verbatiminput{experiment/Lang-2} \\
    \hline
    \textbf{``Range''} & \textbf{``Optional''} \\[-2ex]
    \verbatiminput{experiment/Range-2} & 
    \verbatiminput{experiment/Optional-2}\\
    \hline
  \end{tabular}
\end{center}
These fragments has been carefully designed for illustrative utility,
as well as suitable selectivity. They are not themselves important,
they only serve to illustrate certain examples of possible
factors. When the experiment is run, they are combined to yield a
query, which is then sent to a SPARQL endpoint. The SPARQL endpoint is
itself set up using 4store (see \cite{harris20094store}) version
1.1.5. The ``Machine'' factor specifies a hostname, whereas
``TripleC'' and ``Implement'' specifies a port number. On each host,
four 4store instances runs sequentially and independently on different
ports, where processes that are not actively answering a query are
idle.

@@

The experimentation is implemented in R\cite{rmanual}, which is a free
software environment for statistical computing and graphics. Necessary
tools for DoE has been implemented by the R community in packages
called DoE.base\cite{doebase} and FrF2\cite{frf2}. The experiments are
run on a third computer in a 1 gigabit Ethernet LAN with the two
experiment hosts.  As response variable, we have chosen to use the
time from the namespace server lookup finishes to the data has been
transferred. This choice is somewhat arbitrary, many other response
variables could be chosen, and indeed, future work should explore
multi-variable responses, but for simplicity, we think this reflects
the total amount of work done by the SPARQL endpoint well. For the
measurements, we have chosen to use the RCurl package\cite{lang2007r},
which is a thin wrapper around the curl library. Curl has well
developed facilities for timing requests and responses, and so we rely
on its measurements.

>>>>

\begin{center}\small
  \begin{tabular}{|@{~~}p{0.40\textwidth}|@{~~}p{0.53\textwidth}|}
    \hline
    \textbf{``Union''} & \textbf{``Lang''} \\[-2ex]
    \verbatiminput{experiment/Union-2} &
    \verbatiminput{experiment/Lang-2} \\
    \hline
    \textbf{``Range''} & \textbf{``Optional''} \\[-2ex]
    \verbatiminput{experiment/Range-2} & 
    \verbatiminput{experiment/Optional-2}\\
    \hline
  \end{tabular}
\end{center}
These fragments has been carefully designed for illustrative utility,
as well as suitable selectivity. They are not themselves important,
they only serve to illustrate certain examples of possible
factors. When the experiment is run, they are combined to yield a
query, which is then sent to a SPARQL endpoint. The SPARQL endpoint is
itself set up using 4store (see \cite{harris20094store}) version
1.1.5.

@@

The experimentation is implemented in R\cite{rmanual}, which is a free
software environment for statistical computing and graphics. Necessary
tools for DoE has been implemented by the R community in packages
called DoE.base\cite{doebase} and FrF2\cite{frf2}. The experiments are
run on a third computer in a 1 gigabit Ethernet LAN with the two
experiment hosts. On the experiment hosts, four 4store instances runs
sequentially and independently on different ports, where processes
that are not actively answering a query are idle. Practically, the
``Machine'' factor specifies a hostname, whereas ``TripleC'' and
``Implement'' specifies a port number. On each host,

As response variable, we have chosen to use the time from the
namespace server lookup finishes to the data has been
transferred. This choice is somewhat arbitrary, many other response
variables could be chosen, and indeed, future work should explore
multi-variable responses, but for simplicity, we think this reflects
the total amount of work done by the SPARQL endpoint well. For the
measurements, we have chosen to use the RCurl package\cite{lang2007r},
which is a thin wrapper around the curl library. Curl has well
developed facilities for timing requests and responses, and so we rely
on its measurements.
